Flowchart of Current Algorithm

### 2008-10-24 docs/flowchart/flowchart.tex
put in placeholders for Advect Base Density, Advect Base Pressure, and Advect Base Enthalpy

\item {\bf Correct Base}
$[\rho_0^{\inp}, (\nabla\cdot\etarho\er)^{\inp}] \rightarrow [\rho_0^{\outp}]$\\
is the process by which we adjust the base state density to account for
large-scale mixing, through $\etarho$.  For both plane-parallel and spherical
we use
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \dt (\nabla\cdot\etarho\er)^{\inp}_j \enskip . 
\end{equation}

@@

\item {\bf Advect Base}$[\rhozero^{n}, (\rho h)_0^{(1)}, p_0^{n}, \beta_0^{(1)}, w_0^{\nph,\star}, \psi^{\nmh}] \rightarrow $
$[\rho_0^{(2),\star}, (\rho h)_0^{(2),\star}, \rho_0^{\nph,\star,{\rm pred}}, p_0^{n+1,\star}].$

@@

@@

@@

\item {\bf Correct Base}
$[\rho_0^{(2),\star}, (\nabla\cdot\etarho\er)^{\nph,*}] \rightarrow [\rho_0^{n+1,\star}]$.

@@

\item {\bf Advect Base}$(\rho_0^{n}, (\rho h)_0^{(1)}, p_0^{n}, \beta_0^{(1)}, w_0^{\nph}, \psi^{\nph,\star} ) \rightarrow $
$[\rho_0^{(2)}, (\rho h)_0^{(2)}, \rho_0^{\nph,{\rm pred}}, p_0^{n+1}].$

@@

@@

\item {\bf Correct Base}
$[\rho_0^{(2)}, (\nabla\cdot\etarho\er)^{\nph}] \rightarrow [\rho_0^{n+1}]$

>>>>

\item {\bf Correct Base}$[\rho_0^{\inp}, (\nabla\cdot\etarho\er)^{\inp}] \rightarrow [\rho_0^{\outp}]$\\
is the process by which we adjust the base state density to account for
large-scale mixing, through $\etarho$.  For both plane-parallel and spherical
we use
\begin{equation}
\rho_{0,j}^{\outp} = \rho_{0,j}^{\inp} - \dt (\nabla\cdot\etarho\er)^{\inp}_j \enskip . 
\end{equation}

@@

%\item {\bf Advect Base}$[\rhozero^{n}, (\rho h)_0^{(1)}, p_0^{n}, \beta_0^{(1)}, w_0^{\nph,\star}, \psi^{\nmh}] \rightarrow [\rho_0^{(2),\star}, (\rho h)_0^{(2),\star}, \rho_0^{\nph,\star,{\rm pred}}, p_0^{n+1,\star}].$

\item {\bf Advect Base Density}

@@

\item (spherical only) {\bf Advect Base Pressure}

@@

\item (plane-parallel only only) {\bf Advect Base Pressure}

\item {\bf Advect Base Enthalpy}

@@

\item {\bf Correct Base}$[\rho_0^{(2),\star}, (\nabla\cdot\etarho\er)^{\nph,*}] \rightarrow [\rho_0^{n+1,\star}]$.

@@

%\item {\bf Advect Base}$(\rho_0^{n}, (\rho h)_0^{(1)}, p_0^{n}, \beta_0^{(1)}, w_0^{\nph}, \psi^{\nph,\star} ) \rightarrow [\rho_0^{(2)}, (\rho h)_0^{(2)}, \rho_0^{\nph,{\rm pred}}, p_0^{n+1}].$

\item {\bf Advect Base Density}

@@

\item (plane-parallel only) {\bf Advect Base Pressure}

\item {\bf Advect Base Enthalpy}

@@

\item {\bf Correct Base}$[\rho_0^{(2)}, (\nabla\cdot\etarho\er)^{\nph}] \rightarrow [\rho_0^{n+1}]$
